---
title: "Focal plane wvaefront sensor data anaylsis"
output:
  html_document:
    df_print: paged
---



```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(R.matlab)
library(caret)
library(corrplot)
library(xtable)
#library(oetteR)
library(caret)
library(rrr)
library(feather)

```



```{r echo=FALSE, message=FALSE, warning=FALSE}
# Read in .mat file
data <- readMat("data/PLWFS_labdata_61219.mat") 

namesZernike <- paste0("zernikeCoeef", seq(1:dim(data$zernike.coeffs)[[2]]))
namesFlux <- paste0("FluxCoeef", seq(1:dim(data$output.fluxes)[[2]]))

zernikeData <- data$zernike.coeffs %>% as_tibble() %>% set_names(namesZernike)
zernikeLong <- pivot_longer(zernikeData, cols = starts_with("z"), names_to = "Coefficient", values_to = "value")

fluxData <- data$output.fluxes %>% as_tibble() %>% set_names(namesFlux)
fluxLong <- pivot_longer(fluxData, cols = starts_with("F"), names_to = "Coefficient", values_to = "value")

write_feather(zernikeData, "data/zernikeData.feather")
write_feather(fluxData, "data/fluxData.feather")
AoData <- bind_cols(zernikeData, fluxData)

```

# An all-photonic focal-plane wavefront sensor

Working on AO based on data of Sydney Institute for Astronomy, School of Physics, University of Sydney, from the paper "An all-photonic focal-plane wavefront sensor"


# Investigation of data

Look at the distributions 

## Zernike coefficients
There is no expected distribution of the zernikie coefficients.

```{r echo=FALSE, message=FALSE, warning=FALSE}


zernikeLong %>% ggplot(aes(value, fill = Coefficient)) + geom_histogram() + facet_wrap(vars(Coefficient))


```

The observed distribution 

## Flux data

Now flux outputs 

```{r echo=FALSE, message=FALSE, warning=FALSE}


fluxLong %>% ggplot(aes(value, fill = Coefficient)) + geom_histogram() +scale_y_log10() + facet_wrap(vars(Coefficient)) 




fluxLong %>% ggplot(aes(value, fill = Coefficient)) + geom_histogram() + facet_wrap(vars(Coefficient)) 


```



## Find correlations
### Find high correlations

```{r echo=FALSE, message=FALSE, warning=FALSE}


descrCor <- cor(AoData)



highlyCorDescr <- findCorrelation(descrCor, cutoff = .62)
filteredAoData <- AoData[,highlyCorDescr]

filteredAoDataCor <- cor(filteredAoData)

corrplot(filteredAoDataCor)

```


### as table
```{r echo=FALSE, message=FALSE, warning=FALSE}


upper<-cor(filteredAoData) %>% round(2)
upper[upper.tri(cor(filteredAoData))]<-""
upper<-as.data.frame(upper)
upper

```

### Overview of all correlations

```{r echo=FALSE, message=FALSE, warning=FALSE}



corrplot(descrCor)

```

Since there is no strong correlation we can use tree algorithms




# Tree based regression


## regression with caret - multivariate adaptive regression splines (MARS)

According to https://rstudio-pubs-static.s3.amazonaws.com/376822_e229bf5a5d574f7c93e12cb524f726f1.html

 Register CPU cores

```{r echo=FALSE, message=FALSE, warning=FALSE}
#library(parallel)
library(doParallel)
cluster <- makeCluster(detectCores() - 1) ## convention to leave 1 core for OS
registerDoParallel(cluster)

```

## Random forest
According to https://stats.stackexchange.com/questions/404054/r-multivariate-random-forest-for-variable-importance a multivariant regression can be calculated with pacakge randomForestSRC

multivar_fit<-rfsrc(cbind(y1,y2,y3,y4)~.,data=bays_data)

multivar_fit<-rfsrc(zernikeData~.,data=fluxData)

```{r}
library(randomForestSRC)
set.seed(2021)
train <- sample(1:nrow(AoData), round(nrow(AoData) * 0.80))
AoData.grow <- rfsrc(cbind(zernikeCoeef1, zernikeCoeef2, zernikeCoeef3, zernikeCoeef4, zernikeCoeef5, zernikeCoeef6, zernikeCoeef7, zernikeCoeef8, zernikeCoeef9)~., AoData[train, ], ntree =1000)
AoData.pred <- predict.rfsrc(AoData.grow, AoData[-train , ]) 
print(AoData.grow)
print(AoData.pred)

#predValues <- AoData.pred[["yvar"]]

#errorPredVsTest <- predValues-AoData[-train , ] %>% select(zernikeCoeef1, zernikeCoeef2, zernikeCoeef3, zernikeCoeef4, zernikeCoeef5, zernikeCoeef6, zernikeCoeef7, zernikeCoeef8, zernikeCoeef9)

plot(AoData.grow)


errZernikeCoeef1 <- AoData.pred[["regrOutput"]][["zernikeCoeef1"]][["predicted"]] -  AoData[-train ,"zernikeCoeef1" ] %>% set_names("errorPredTest")
errZernikeCoeef2 <- AoData.pred[["regrOutput"]][["zernikeCoeef2"]][["predicted"]] -  AoData[-train ,"zernikeCoeef2" ] %>% set_names("errorPredTest")
errZernikeCoeef3 <- AoData.pred[["regrOutput"]][["zernikeCoeef3"]][["predicted"]] -  AoData[-train ,"zernikeCoeef3" ] %>% set_names("errorPredTest")
errZernikeCoeef4 <- AoData.pred[["regrOutput"]][["zernikeCoeef4"]][["predicted"]] -  AoData[-train ,"zernikeCoeef4" ] %>% set_names("errorPredTest")
errZernikeCoeef5 <- AoData.pred[["regrOutput"]][["zernikeCoeef5"]][["predicted"]] -  AoData[-train ,"zernikeCoeef5" ] %>% set_names("errorPredTest")
errZernikeCoeef6 <- AoData.pred[["regrOutput"]][["zernikeCoeef6"]][["predicted"]] -  AoData[-train ,"zernikeCoeef6" ] %>% set_names("errorPredTest")
errZernikeCoeef7 <- AoData.pred[["regrOutput"]][["zernikeCoeef7"]][["predicted"]] -  AoData[-train ,"zernikeCoeef7" ] %>% set_names("errorPredTest")
errZernikeCoeef8 <- AoData.pred[["regrOutput"]][["zernikeCoeef8"]][["predicted"]] -  AoData[-train ,"zernikeCoeef8" ] %>% set_names("errorPredTest")
errZernikeCoeef9 <- AoData.pred[["regrOutput"]][["zernikeCoeef9"]][["predicted"]] -  AoData[-train ,"zernikeCoeef9" ] %>% set_names("errorPredTest")


totalErr <- bind_rows(errZernikeCoeef1,
errZernikeCoeef2,
errZernikeCoeef3,
errZernikeCoeef4,
errZernikeCoeef5,
errZernikeCoeef6,
errZernikeCoeef7,
errZernikeCoeef8,
errZernikeCoeef9,
)






sqrt(sum(totalErr^2)/nrow(totalErr))
```
